Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-08 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] changed caption of fig 3 and text in section IV.C

Here we describe the theoretical treatment of observables and collect
numerical input of the most relevant parameters. The software package
{\tt EOS} \cite{Bobeth:2011gi, Bobeth:2011nj, EOS} is used for
predictions of observables in $B_s\to \bar\mu\mu$ and $B\to
K^{(*)}\bar\ell\ell$. The fit is performed with the package {\tt
  pypmc}, which incorporates the algorithm presented in
\cite{Beaujean:2013:PMC, Beaujean:2012uj} and in addition an
implementation of the variational Bayes algorithm. \fred{Add, get DOI
  for pypmc version}

>>>>

Here we describe the theoretical treatment of observables and collect numerical
input of the most relevant parameters. The software package {\tt EOS} \cite{Bobeth:2011gi,
Bobeth:2011nj, EOS} is used for predictions of observables in $B_s\to \bar\mu\mu$
and $B\to K^{(*)}\bar\ell\ell$. The fit is performed with the package {\tt pypmc},
which incorporates the algorithm presented in \cite{Beaujean:2013:PMC, Beaujean:2012uj}
and in addition an implementation of the variational Bayes algorithm.
